---
title: "Geog533 Lab 8"
author: "Yalin Yang"
output: 
  html_notebook:
    toc: TRUE
    toc_float: TRUE
---

Complete the following exercises in Chapter 8 (Introduction to Regression Analysis) of the textbook [R] pages 247-250. 

## Question 1

This is Exercise 1 in Chapter 8 of the Textbook [R].

A regression of weekly shopping trip frequency on annual income (data entered in thousands of dollars) is performed on data collected from 24 respondents. The results are summarized below:

* Intercept: 0.46
* Slope: 0.19

|          | Sum of squares  | Degrees of freedom |  Mean square   |       *F*       |
|----------|-----------------|--------------------|----------------|-----------------|
|Regression|     `r 2.3-1.7` |          1         | `r (2.3-1.7)/1`|`r (2.3-1.7)/1/(1.7/(24-2))`|
| Residual |       1.7       |        `r 24-2`    | `r 1.7/(24-2)` |                 |
| Total    |       2.3       |        `r 24-1`    |                |                 |


### Question 1(a)
Fill in the blanks in the ANOVA table.

```{r}
```


|          | Sum of squares  | Degrees of freedom |  Mean square   |       *F*       |
|----------|-----------------|--------------------|----------------|-----------------|
|Regression|  `r 2.3-1.7` |          1            | `r (2.3-1.7)/1`|`r (2.3-1.7)/1/(1.7/(24-2))`|
| Residual |       1.7       |        `r 24-2`    | `r 1.7/(24-2)` |                 |
| Total    |       2.3       |        `r 24-1`    |                |                 |



### Question 1(b)
What is the predicted number of weekly shopping trips for someone making $50,000/year?
```{r}
Shop_time <- 0.19*50+0.46
print(paste('the predicted number of weekly shopping trips is',Shop_time))
```


### Question 1(c)
In words, what is the meaning of the coefficient 0.19?
```{r}
print('There was a positive correlation between independent variables and dependent variables, when independent variables changes 1, the dependent variable will change 0.19')
```



### Question 1(d)
Is the regression coefficient significantly different from zero? How do you know?
```{r}
one_F <- (2.3-1.7)/1/(1.7/(24-2))
if(one_F > qf(0.95,df = 1,df2 = 22))
{
  print('it is significant beacuse the F value in the rejection area')
  
}
```



### Question 1(e)
What is the value of the correlation coefficient?
```{r}
one_F <- (2.3-1.7)/1/(1.7/(24-2))
r2 <- (24-2)/one_F + 1
R <- sqrt(1/r2)
R
```





## Question 2

This is Exercise 6 in Chapter 8 of the Textbook [R].

The following data are collected in an effort to determine whether snowfall is dependent upon elevation: 

| Snowfall (inches) | Elevation (feet) |
|-------------------|------------------|
|       36          |       400        |
|       78          |       800        |
|       11          |       200        |
|       45          |       675        |

Using R, show your work on exercises (a) through (g).

### Question 2(a)
Find the regression coefficients (the intercept and the slope coefficient).
```{r}
y <- c(36,78,11,45)
x <- c(400,800,200,675)
m <- lm(y~x)
slope <- m$coefficients[2][[1]]
intercept <- m$coefficients[1][[1]]
print(paste('intercept is ',round(intercept,4) ,'and slope is ',round(slope,4)))
```


### Question 2(b)
Estimate the standard error of the residuals about the regression line.
```{r}
a <- summary(m)
summary(m)
sd.err<- sqrt(sum((a$residuals - mean(a$residuals))^2)/(4-2))
print(paste('the standard error of the residuals is ',round(sd.err,digits = 5)))

```


### Question 2(c)
Test the hypothesis that the regression coefficient associated with the independent variables is equal to zero. Also place a 95% confidence interval on the regression coefficient.
```{r}
result <- anova(m)
if (result$`Pr(>F)`[1] > 0.05)
{
  print('it is not signigicant')
}
```


### Question 2(d)
Find the value of $r^2$.
```{r}
result.err<- cor.test(x,y,method = 'pearson')
R <- (result.err$estimate[[1]]^2)
R
```


### Question 2(e)
Make a table of the observed values, predicted values, and the residuals.
```{r}
b <- summary(m)
df <- data.frame(y,fitted(m),b$residuals)
head(df)
```


### Question 2(f)
Prepare an analysis of variance table portraying the regression results.
```{r}
anova(m)
```


|          | Sum of squares  | Degrees of freedom |  Mean square   |       *F*       |
|----------|-----------------|--------------------|----------------|-----------------|
|Regression|      195094     |         1          |    195094      |       16.173    |
| Residual |       24125     |        2           |      12063     |                 |
| Total    |      219219     |                    |                |                 |

### Question 2(g)
Graph the data and the regression line.
```{r}
plot(x,y)
abline(m,col='red')
```




## Question 3

This is Exercise 10 in Chapter 8 of the Textbook [R].

Use R and the [Milwaukee dataset](http://spatial.binghamton.edu/geog533/data/Milwaukee_Sales.csv) to:

### Problem
perform a regression using sales price as the dependent variable and lot size as the independent variable.

### Solution
```{r}
url = "http://spatial.binghamton.edu/geog533/data/Milwaukee_Sales.csv"
df <- read.csv(file = url)
X <- df$SalePrice
Y <- df$LotSize
plot(X,Y)
M<- lm(Y~X)
abline(M,col='red')
```



## Question 4

This is Exercise 11 in Chapter 8 of the Textbook [R].

Use R and the Hypothetical [UK Housing Prices dataset](http://spatial.binghamton.edu/geog533/data/UK_Housing.csv) to:

### Question 4(a) 
perform a regression using house price as the dependent variable, and number of bedrooms as the independent variable;

```{r}
url = "http://spatial.binghamton.edu/geog533/data/UK_Housing.csv"
df_new <- read.csv(file = url)
p <- df_new$price
o <- df_new$bedrooms
m <- lm(p~o)
equa<- paste('Y = ',round(m[[1]][[1]],digits = 0),'+',round(m[[1]][[2]],digits = 0),'X')
plot(o,p,main = equa,ylab = 'The price of House',xlab = 'The number of bedrooms')
abline(m,col='red')
```


### Question 4(b) 
(b) repeat part (a), using the number of bathrooms as the independent variable, and comment on the results.
```{r}
df_new <- read.csv(file = url)
j <- df_new$price
k <- df_new$bathrooms
m_new <- lm(j~k)
equa_new <- paste('Y = ',round(m_new[[1]][[1]],digits = 0),'+',round(m_new[[1]][[2]],digits = 0),'X')
plot(k,j,main = equa_new,ylab = 'The price of House',xlab = 'The number of bathrooms')
abline(m,col='red')
```


## Question 5
Download the [hometown.csv](http://spatial.binghamton.edu/geog533/data/hometown.csv), append your name and hometown coordinates to the csv, then use [leaflet](https://rstudio.github.io/leaflet/) to create a web map (10 pt.)

```{r}
url = 'http://spatial.binghamton.edu/geog533/data/hometown.csv'
df_yyl <- read.csv(file = url)
fix <- c('yang','yalin','grads','106.481,29.590','106.481','29.590','','','')
df_yyl <- as.data.frame(rbind(as.matrix(df_yyl) , fix))
df_yyl[25:34,]
library(leaflet)

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=106.481, lat=29.590, popup="The birthplace of R")
m 
```

