---
title: "Geog533 Lab 10"
author: "Yang_Yalin"
output: 
  html_notebook:
    toc: TRUE
    toc_float: TRUE
---

## Question 1
Use R package UScensus2010county to complete the following tasks:  (20 pt.)

### Question 1(a)
Plot a map of New York counties using the plot function.
```{r echo=FALSE}
library(rgeos)
library(UScensus2010)
library(UScensus2010county)
library(UScensus2010tract)
data("new_york.county10")
shp<- new_york.county10
plot(shp)
```

### Question 1(b)	
Plot a map of New York counties using the qtm function.
```{r}
library(tmap)
qtm(shp,fill = "P0010001")
```


### Question 1(c)	
How many counties in New York State?
```{r}
df <- shp@data
nc <- table(df$county)
nrow(nc)
```

### Question 1(d)	
What’s the 3-digit fips code of Broome County?
```{r}
data(countyfips)
df_fips <- countyfips[countyfips$statename == "new_york",]
fips.code <- df_fips[df_fips$countyname == 'broome county',]['fips']
fips <- gsub('\\s+','',paste("00",as.numeric(fips.code[[1]][1]) %% 100))
fips
```

### Question 1(e)	
Compute descriptive statistics of the population column (P0010001), including total, minimum, maximum, mean, median, and skewness. 
```{r}
library(moments)
sum(df$P0010001)
summary(df$P0010001)
skewness(df$P0010001)
```

### Question 1(f)	
Create a histogram and a boxplot of the population.
```{r}
hist(df$P0010001)
```

```{r}
boxplot(df$P0010001)
```

## Question 2
Use R package UScensus2010tract to complete the following tasks:    (20 pt.)


### Question 2(a)	
Plot a map of New York census tracts using the plot function.
```{r}
data("new_york.tract10")
shp_new <- new_york.tract10
plot(shp_new)
```

### Question 2(b)
Compute the total population based on census tracts.
```{r}
data_p <- shp_new@data
sum(data_p$P0010001)
```

### Question 2(c)
Select all census tracts in Broome County and plot the map. 
```{r}
shp_broome <- shp_new[shp_new$county == '007',]
plot(shp_broome)
```

### Question 2(d)
What’s the total population of Broome County?
```{r}
df_broome <- shp_broome@data
sum(df_broome$P0010001)
```

### Question 2(e)
Create a histogram and a boxplot of population based on census tracts of Broome County.
```{r}
hist(df_broome$P0010001)
```
```{r}
boxplot(df_broome$P0010001)
```

### Question 2(f)
Select the first five columns of the shapefile of Broome County census tract; add a new population ratio column (= census tract population / county population); save the new shapefile to the hard drive. 
```{r}
library(rgdal)
shp_write <- shp_broome[,1:5]
shp_write
df_write <- shp_write@data
df_write$ratio <- df_write$P0010001/sum(df_broome$P0010001)
shp_write@data <- df_write
writeOGR(shp_write,dsn = "output",layer = "shp_write",driver = "ESRI Shapefile",overwrite_layer = TRUE)
shp_read <- readOGR(dsn = "output", layer = "shp_write")
```


## Question 3

Use R packages raster and ncdf4 to complete the following tasks:     (20 pt.)


### Question 3(a)		
Load the multi-band raster dataset “NDVI.nc??? into R.
```{r}
library(ncdf4)
library(raster)
ndvi <-  brick("NDVI.nc")
plot(ndvi)
```

### Question 3(b)		
Get the basic information about the dataset, including the number of rows, columns, cells, and bands; spatial resolution, extent, bounding box, and projection.
```{r}
nrow(ndvi)
ncol(ndvi)
ncell(ndvi)
extent(ndvi)
bbox(ndvi)
res(ndvi)
projection(ndvi)
ndvi@file@nbands
```

### Question 3(c)	
Aggregate all bands to generate a mean NDVI raster and a maximum NDVI raster; save the two new raster datasets to the hard drive. 
```{r}
ndvi.rb <- brick("NDVI.nc")
ndvi.rb.mean <- mean(ndvi.rb)
ndvi.rb.max <- max(ndvi.rb)
plot(ndvi.rb.max)

```

### Question 3(d)			
Plot the maps of monthly NDVI of the year 2001
```{r}
plot(ndvi.rb[[13:24]])
ndvi.rb
```

### Question 3(e)	
Create histograms of monthly NDVI of the year 2001.
```{r echo=FALSE}
hist(ndvi.rb[[13:24]])
```

### Question 3(f)			
Plot the NDVI map of July 2000; click any location with data on the map and retrieve the NDVI time series for all years; plot the NDVI time series of the selected location. 
```{r}
plot(ndvi.rb,7)
value <- ndvi.rb[50,50]
plot(as.vector(value), type="b")
```


